D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-06 ootavacuous.tex
C++ implementations need not use cbmc/nidhugg/whatever
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

However, as will be seen in later sections, in some special but
commonly occurring circumstances, much simpler methods exist.

>>>>

All of these tools can incur high overhead, especially manual code
inspection.
However, as we will see, C++ implementations need not use these tools.
Their current analysis is guanteed to be sufficient.
Furthermore, as we will also see, in some special but commonly occurring
circumstances, much simpler methods exist that incur negligible overhead.
